\documentclass{book}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a5paper, left=20mm, right=20mm, top=10mm}
\pagenumbering{gobble}
\begin{document}
%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%
%The first chapter - Dawn's first nightmare the readers see - Akbar's first dialouge of speech
%\paragraph*{I promise to write one page and draw everyday.\\\\I promise to immortalise her in pen.\\\\I promise the whole world one day will know all the amazing things about her.\\\\How her face beams when she's happy and her eyes become crescent moons.\\\\How she puts on a brave face of optimism in the worst of days.\\\\How she's always there for me when I feel my world begin to collapse.\\\\How she was and always will exist in my world.\\\\I couldn't keep anything else... and I don't deserve her again.\\\\I still promise, to write and draw everything.\\\\The memories hurt less that way, but more importantly its for her.\\\\The friendship and memories captured}
%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%
\chapter{Dream sequence, while paralysed}
\paragraph{The alarm bell rang.\\\\Rring Rring! Rring Rring!\\\\Its giant arms and steel fists were cocked back like a revolver - ready to fire its empty rounds -into empty space.\\\\Rring Rring! Rring Rring! The rounds ricocheted of walls and bounced back into my eardrum - rattling the ins and outs of my spry skull. The ringing grew and a series of post-it notes, tacked to the wall, were sent fluttering to the floor. Then so did a row of glass beer bottles, causing an awful clank as they rolled past each other. And a glass picture frame. The final victim to the alarms tirade\\\\Rring Rring! Rring Rring!\\\\The ringing ceased to stop and I felt each and every vibration creep its way up my spine. My eyes, glued to the side but wide-open faced the empty wall, waiting. Waiting for the ringing to subdue.\\\\Rring Rring! Rring Rring!\\\\It hadn't stopped and my bed which has been sitting in the far corners of my room soon began to give into the alarms demands.\\\\Stretching.\\\\Sinking.\\\\And slumping to the alarms metronome.\\\\I was to follow suite.}


%Dream
\paragraph{\textit{The city's surrounded itself. Mute-grey skyrises, clad with their concrete armour and windowless stares. They litter the streets at regular intervals - but never seem to end. Busy bodies with airbrushed faces brush past you - disappearing past the bend. A whistles been blown, the noise slashes at the heavy blanket of day and a taxi promptly arrives. The honk of a horn, red light, red light and a cop car quickly drives. Follow this maze of streets and you'll quickly discover the web of veins pumping vitality to its heart.\\\\As I flick through my phone scrolling up and down, I accidentally lock eyes with a thin spectacled man in a striped suit walking down the boulevard. I decide to match my pacing with his, in hopes he'll direct me to the correct location. He walks faster. I walk faster. He walks faster. I walk faster. A thin bead of sweat trickles down his forehead and he stops abruptly.\\\\``Hi I was just wondering if you knew where -\\\\10 seconds pass. Then another 10. He stares deep into my eyesockets as if he's seen a ghost.\\\\``No, you're not him I must be mistaken'' he whispers, running frantically down the busy street opposite the way he came.\\\\The fuck is wrong with him, probably a looney, I mumble. As I trace my steps back to my starting position, I catch wift of a pungent odour. Sealing my mouth shut, my eyes are met with a horrid bright blue neon sign.\\\\WELCOME TO SMOKERS LOUNGE! Smoking prohibited outside of lounge.\\\\``Smokers lounge'' I tut to myself, ``anything but a lounge''. It was one of the locations I had seen on my phone, so I knew I had to be close. ``Filthy, filthy, filthy'' I mutter as I walk towards the sign. Mist forms above my cold breath and I backtrck a few steps. All different walks of life are huddled in one large group, as if they were a colony of penguins clinging to the last remnants of winter warmth. Blue, collar, white-collar, red-collar. Yep they're all here. To each their own, I say but if it wasn't for their wide-eyed smiles and gigantic grins I wouldn't have stopped and stared. Rows of men and women sprawl across a small patch of grass. Office worker, construction worker, office worker, sanitation worker.\\\\Yet....\\\\This crowd... they're happy? I can make out their middle aged banter and chuffed expression through the waft of cigartte smoke. And there doesn't seem to be a care in their eyes. They all seem so happy, so young, so yout-\\\\Honk!\\\\No I say to myself. They've got yellowish stained teeth, black lungs and a burning hole in their wallet. Honk! Another car speeds towards the closing green light and the waft of smoke disappears before my eyes.\\\\``Filthy, filthy'' I mutter.}}
\paragraph{\textit{The city's surrounded itself. Mute-grey skyrises, clad with their concrete armour and windowless stares, litter the streets at regular intervals. Busy bodies with their airbrushed faces, brush past you - never to be seen again. A whistles blown, the noise slashing the heavy blanket of day, and a taxi promptly arrives. The toot of a horn, red light, red light, and a taxi quickly drives. Follow this maze of steets, and you'll discover the web of veins pumping vitality to its heart.\\\\As I flick through the map on my phone, to figure out where I am exactly, I catch wift of an awful smell. Clasping my mouth shut with my hands, my eyes are meet with a horrid bright blue neon sign.\\\\WELCOME TO SMOKERS LOUNGE! SMOKING PROHIBITED OUTSIDE OF LOUNGE.\\\\``Smokers lounge'' I tut to myself anything but a lounge. ``Filthy, filthy, filthy'' I mutter. Mist forms above my cold breath and I backtrack a few steps. All different walks of life seem to be huddled together clinging to the last remnants of warmth. One big group all chummed up. Blue-collar, white-collar, red-collar. Yep they're all here. To each their own, I say but if it wasn't for their wide-eyed smiles and gigantic grins I wouldn't have stopped and stared. Rows of men and women sprawled across a small patch of grass. Office worker, construction worker, office worker, sanitation worker.\\\\Yet...\\\\This crowd... they're happy? Their middle aged banter and chuffed expressions can be seen through the waft of ciggarette smoke. And there doesn't seem to be a care in their eyes. They all seem so happy, so young, so yout-\\\\Honk.\\\\No. They have stained teeth, black lungs and a burning hole in their wallet, I say to myself as a speeding car clears away the waft of smoke before my eyes.l}}
\paragraph{A ballad of branches lurking amidst the shadows crawled up into the air. Floating in the air they clattered their skeleton bones tearing away at the windowill.\\\\Tip-tap tip-tap.\\\\As if it was a signal, the wind was on cue. Weaving, its way through the rowdy crowd the wispy wind pushed past needle-like branches slipping an eerie lullaby inbetween the cracks.}
\paragraph{Lurking amidst shadows, a ballad of branches begins to creep out from their hiding. Clattering, their skeleton bone gently float in the wind and gently tap away at my windowsill.\\Tip-Tap. Tip-Tap.\\Weaving its way inwards, the wispy wind pushed past needle-like branches only to slip an eerie lullaby through curtain gaps.}

%Dream
\paragraph{\textit{``Pardon me sir, we're here to search your belongings'' comes a brawny voice.\\\\``No, stop that tickles'' a voice shrieks.\\\\``Aaah no stop! stop! that's my heart! my actual heart!''.\\\\``Sir, we'll need to search your belongins''.\\\\``Sure'' I reply. He grabs it from my frail hands and unclasps it at once. \textbf{He didn't ask for the combination... He didn't ask!}\\\\``Hey, that's mine, that's mine!''. I watch in horror, blank face and all as I watch a black sketchbook adorned with childrens drawings float down the gutter.\\\\``You asshole!'' I curse raising my fists. Before I can finish, my eyes meet the gorilla faced security guard before me. He flashes a shark smile and grabs my collarbone}}

%Snap back to reality \paragraph{An ordeal through hell itself; 10 rounds with the king of the nightmare world and an unstoppable alarm. ``A silly smile snuck its way onto h-''. ``What caught the eughh eye's'' he mumbled.\\\\Thump!\\\\Falling ever so gracefully onto the cold hardwood floor he remained. Oblivous to the sounds of the alarm, he remained. Still muttering those same lines.}
%Wakes up from the dream

\paragraph{I lie still for a while. Breathing in slowly. Breathing out slowly. ``How long was I out for''. The shutters are drawn. Morning's arrived. I can hear a faint clatter of dishes and a jingle of keys. Yonder and a ritual silence. I let out a deep moan. I can feel the stiffness building up in my neck. Rain. Rain. Training to make my entire life a misery but it only remains as frozen dew and it seems to have been an eternity since I've heard the birds chirp. I think to myself... as my mind wanders. ``How long was I out for? And why am I on the floor?''. Last night at the bar... \textit{How much did I fucking drink?} I presumed the others would be hungover from last nights rounds, guess I was wrong. Fuck. I know my rooms less shielded from the elements, it was built that way. Still, it feels like this weathers got a personal vendetta against me. Maybe that's sums up why I've been struggling to get a full nights rest. Well that coupled with my: drinking habit, manga addiction and porno fix.}



\paragraph{Gently leaning to my side, I felt the smooth-cold touch of the hardwood floor against my bare skin. My eyes began to drift around vaguely as I recollected the events that transpired last night. I let out a sombre yawn and ponder as to what the time is. As I raise my arms triumphantly to mark the start of what was sure to be a busy day I feel a frail and long hand gently lower them. He turns my chin. I meet a pair of blackbird eyes}
\paragraph{``Did you lose your sense of sight to, when you fell?'' a familiar voice coldy inquires.}
\paragraph{``No I can see just fine!'' I reassure the voice, beaming back but squinting ever so slightly so I didn't give away I had no idea who I was speaking to.}
\paragraph{``Good, good''.}
\paragraph{A minute passes. Then another. He sits and gently shifts thorugh my wreckage of a bed. The floor, still cold beneath his feet. He's taller and his clothing much darker than mine. 30 seconds pass and he pivots to the side. Light seeps throgh shutter gaps alligning itself in perfect panels on my hardwood floor. He slips a smirk and gravitates towards me. Another 30 seconds go by and he taps at the floor. A smile crawls up the sides of his face and he quickly purses his lips.}
\paragraph{`` Ermm sur-.}
\paragraph{Before I can finish, I feel my phone screen being squished between my face. As I wrestle with the voice, I feel the shutters of my eyes go mad, as the glaring screen comes closer, burning the edges of my eyes}
\paragraph{``Aaah fuck off'' I yell.}
\paragraph{``Read it!''  he snaps back.}
\paragraph{``Not until, you get of me''}
\paragraph{Thump!}
\paragraph{A fuzzy neon hue melts into my eye.}
\paragraph{Seven. Fourty five. AM ``HOLY SHIT''.}
\chapter{School}
\paragraph{It was a woeful early winter morning. The busy town of Solstice was mute-grey and void of all life; except for the scurry of morning delivery. As I trudged through through heavy wades of snow I chuckled to myself.}
\paragraph{\textit{Why did Akbar have to be such an early bird? And why did it fuckign matter if I was late or not - its not like we go 2 class together}}
\paragraph{Then again if he hadn't been my personal alarm I would have definetely missed my first class of semester and I didn't want to get in my teacher's bad books on the very first day either. Shame, he couldn't chauffer me to class though. I'll make it up to him. I'll buy him something from the convenience store, probably a cola or iced beer. But that thought would have to be put on hold.}
\paragraph{A stalker. It'd been tailing me for long enough. It circled around my small frame in a figure of eight. desperate to break into my balloon lungs, it blew a huge gust of gritty gale into my mouth. I gagged involuntarily as I felt each and every corner of my lungs filling with shards of winter air.}
\paragraph{\textit{Less than a month. The cute weather girl said winter would be over in less than a month. I'm gonna write about it. Want something to remember it by}}
\paragraph{As I was induced into a coughing fit, spluttering like a weak engine, I picked up enough conviction to want to leave this horrid weather. It wasn't the first forced kiss with the wind, but it was enough for me to want freedom. Burrowing my chin deep into mybrest, I made one last push to escape this gory wind. ``Its just the usual forecast'' I reassured myself, as I lunged for the closing door handle. As my skinny frame, slipped through the closing glass doors, my marble eyes took one last peak.}
\paragraph{An army of one patrols the street. Smothering the unlit skies, it marches towards us. A carpet of thick black smog is soon to follow. Inch-by-inch. Inch-by-inch, thats what I told myself. The smog and the wind they seem to twirl heavenwards, like they're stealing souls of people caught out in this hellhole}
\paragraph{``Just the usual forecast'' I repeated, more firmly this time. The heated corridor air was far more palatable than the grit left in mouth and the hallways were illuminated by a streak of shining lights. My first day of college, yet I still felt like a highschooler who'd wondered onto campus. Its not that I hadn't been here before. I came on induction day, so the layout of the school was still vaguely familiar to me. Without wasting time, I headed to the library. As I navigated my way down the corridor I was halted by a large blocade.}
\paragraph{``Huh, what's the hold up?'' I inquired, conscious of time.}
\paragraph{``Didn't you hear what happened at the printers?'' replies an anonymous voice.}
\paragraph{``Yeah, I couldn't believe someone like her could pull something like that off''.}
\paragraph{``You think she was set up''.}
\paragraph{``Could be, but I wouldn't shrug the idea she was behind it''.}
\paragraph{``Last time I heard someone did something that scale, they got a whole years worth of detention!''}
\paragraph{``Shit dude, she's totally gonna get expelled then''}



%Her face drops to the ground in an unamused fashion, now if you would please excuse me and leave 

\end{document}

